Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-20 appendix.qmd
Added figure title

## Compute hexbin parameters
num_bins_x_pbmc <- 22

@@

distance_df_small_edges_pbmc <- distance_pbmc |>
  filter(distance < 0.1)#benchmark_pbmc

@@

```{r}
#| echo: false
#| fig-cap: ""
#| label: fig-model-pbmc-author-proj
#| fig-pos: H
#| fig-width: 10
#| fig-height: 15
#| out-width: 90%

>>>>

## Compute hexbin parameters
num_bins_x_pbmc <- 30

@@

@@

```{r}
#| echo: false
#| fig-cap: "Compare the published \\gD{} layout (@fig-pbmc-mse-umap a) and the \\gD{} layout selected (@fig-pbmc-mse-umap b) by MSE plot (@fig-pbmc-mse-umap) from tSNE and UMAP with default hyper-parameters. The PBMC3k data ($n =  5858$) has three clusters in $9\\text{-}D$, where three clusters are close. Two \\gD{} projection from a tour on $9\\text{-}D$ of the model fit with @fig-pbmc-mse-umap a ($a_1 = 0.06$, $b = 616/86 (22, 28)$) shows three-well separated clusters with big separations. On the other hand, the model fit with @fig-pbmc-mse-umap b ($a_1 = 0.06$, $b = 704/227 (22, 32)$) shows three-well separated clusters with small separations. Therefore, @fig-pbmc-mse-umap b is more reasonable than @fig-pbmc-mse-umap a. Videos of the langevitour animations are available at <https://youtu.be/0cKX_HG_n0k> and <https://youtu.be/KhJvsRtaX04> respectively."
#| label: fig-model-pbmc-author-proj
#| fig-pos: H
#| fig-width: 10
#| fig-height: 15
#| out-width: 90%

### 2025-04-20 appendix.tex
Added initial image for Figure 5
Added figure title

>>>>

\includegraphics[width=0.9\linewidth,height=\textheight,keepaspectratio]{appendix_files/figure-pdf/fig-model-pbmc-author-proj-1.pdf}

\caption{\label{fig-model-pbmc-author-proj}Compare the published \gD{}
layout (Figure~\ref{fig-pbmc-mse-umap} a) and the \gD{} layout selected
(Figure~\ref{fig-pbmc-mse-umap} b) by MSE plot
(Figure~\ref{fig-pbmc-mse-umap}) from tSNE and UMAP with default
hyper-parameters. The PBMC3k data (\(n =  5858\)) has three clusters in
\(9\text{-}D\), where three clusters are close. Two \gD{} projection
from a tour on \(9\text{-}D\) of the model fit with
Figure~\ref{fig-pbmc-mse-umap} a (\(a_1 = 0.06\),
\(b = 616/86 (22, 28)\)) shows three-well separated clusters with big
separations. On the other hand, the model fit with
Figure~\ref{fig-pbmc-mse-umap} b (\(a_1 = 0.06\),
\(b = 704/227 (22, 32)\)) shows three-well separated clusters with small
separations. Therefore, Figure~\ref{fig-pbmc-mse-umap} b is more
reasonable than Figure~\ref{fig-pbmc-mse-umap} a. Videos of the
langevitour animations are available at
\url{https://youtu.be/0cKX_HG_n0k} and
\url{https://youtu.be/KhJvsRtaX04} respectively.}

### 2025-04-20 paper.qmd
Added figure title

```{r}
#| echo: false
#| fig-cap: "Compare the published \\gD{} layout (@fig-pbmc-mse a) and the \\gD{} layout selected (@fig-pbmc-mse e) by MSE plot (@fig-pbmc-mse) from the same NLDR with different hyper-parameter choice. The PBMC3k data ($n =  2622$) has three clusters in $9\\text{-}D$, where two of them being close and one separated from the others.  Two \\gD{} projection from a tour on $9\\text{-}D$ of the model fit with @fig-pbmc-mse a ($a_1 = 0.06$, $b = 616/86 (22, 28)$) shows three-well separated clusters with big separations. On the other hand, the model fit with @fig-pbmc-mse e ($a_1 = 0.06$, $b = 704/227 (22, 32)$) shows three-well separated clusters with small separations. Therefore, @fig-pbmc-mse e is more reasonable than @fig-pbmc-mse a. Also, the fitted models in $9\\text{-}D$ help to see some unobserved patterns of the data: (i) dense points, and (ii) non-linear clusters. Videos of the langevitour animations are available at <https://youtu.be/0cKX_HG_n0k> and <https://youtu.be/KhJvsRtaX04> respectively."
#| label: fig-model-pbmc-author-proj
#| fig-pos: H
#| fig-width: 10
#| fig-height: 15
#| out-width: 90%

>>>>

```{r}
#| echo: false
#| fig-cap: "Compare the published \\gD{} layout (@fig-pbmc-mse a) and the \\gD{} layout selected (@fig-pbmc-mse e) by MSE plot (@fig-pbmc-mse) from the UMAP and tSNE with default hyper-parameters. The PBMC3k data ($n =  2622$) has three clusters in $9\\text{-}D$, where two of them being close and one separated from the others.  Two \\gD{} projection from a tour on $9\\text{-}D$ of the model fit with @fig-pbmc-mse a ($a_1 = 0.06$, $b = 616/86 (22, 28)$) shows three-well separated clusters with big separations. On the other hand, the model fit with @fig-pbmc-mse e ($a_1 = 0.06$, $b = 704/227 (22, 32)$) shows three-well separated clusters with small separations. Therefore, @fig-pbmc-mse e is more reasonable than @fig-pbmc-mse a. Also, the fitted models in $9\\text{-}D$ help to see some unobserved patterns of the data: (i) dense points, and (ii) non-linear clusters. Videos of the langevitour animations are available at <https://youtu.be/0cKX_HG_n0k> and <https://youtu.be/KhJvsRtaX04> respectively."
#| label: fig-model-pbmc-author-proj
#| fig-pos: H
#| fig-width: 10
#| fig-height: 15
#| out-width: 90%
